---
title: "DSC 335 Quiz 9"
format: pdf
editor: visual
---

```{r, include=FALSE}
library(tidyverse)
library(bayesrules)
library(gridExtra)
library(rstan)
library(rstanarm)
library(bayesplot)
library(janitor)
library(e1071)
library(broom.mixed)
library(tidybayes) 
```

**Name: Gabriel Eze**

The following code filters the *penguin_bayes* data set so that the *species* variable is binary. We will use this filtered data set *penguin_data* for the problems below.

```{r}
penguin_data <- penguins_bayes %>% 
  filter(species %in% c("Adelie", "Gentoo")) %>%
  na.omit()
```

1.  We are interested in a model that uses the penguin's *species* to predict their body mass, in grams (*body_mass_g*). The only prior information that we want to use (other than default weakly informative priors) is that the typical body mass for Gentoo penguins is 1200 g more than Adelie penguins, but that this difference may be somewhere between 800 and 1600. Fit this model in the code chunk below using the *stan_glm* function.

```{r, results='hide', cache=TRUE}
mod <- stan_glm(body_mass_g ~ species, data = penguin_data, prior_intercept = normal(1200, 200), chains = 4, iter = 10000, seed = 0)
```

2.  Calculate and interpret a 90\\% posterior credible interval for the intercept coefficient in the model.

    ANS: There's a 90% posterior plausibility that the typical body mass in grams of the penguins is between 3571.8 and 3704.0 g.

```{r}
tidy(mod, effects = 'fixed', conf.int = T, conf.level = .9)
```

3.  Perform a 10-fold cross-validation procedure of the model's posterior predictive quality. Produce the standard table of posterior predictive summaries from the cross-validation procedure.

```{r, cache=TRUE}
cv <- prediction_summary_cv(model = mod, data = penguin_data, k = 10)
cv$folds
cv$cv

```

4.  Give an interpretation of the *mae* value from the table above, in context. (If you were unable to produce a table, make up a value and interpret that value as the *mae*.)

ANS: The average mean absolute error from the cross validation of 10 folds is 350.9 g with a fairly small standard error.
