---
title: "DSC 335 Quiz 10"
format: pdf
editor: visual
---

```{r, include=FALSE}
library(tidyverse)
library(bayesrules)
library(gridExtra)
library(rstan)
library(rstanarm)
library(bayesplot)
library(janitor)
library(e1071)
library(broom.mixed)
library(tidybayes) 
```

**Name: Gabriel Eze**

The *fake_news* data in the **bayesrules** package contains information about 150 news articles, some real news and some fake news. The following code runs a logistic regression model that uses the article title's length (*title_words*) and whether the title has an exclamation point (*title_has_excl*) to predict the article *type* (0 is fake news, 1 is real news).

```{r, results='hide'}
q10data <- fake_news %>% 
  mutate(type=as.numeric(type=="real")) %>%
  select(type, title_words, title_has_excl) %>% 
  na.omit()
q10mod1 <- stan_glm(type ~ title_words + title_has_excl, 
                  data = q10data,
                  family = binomial,
                  prior_intercept = normal(1, .4),
                  chains = 4,iter = 5000*2,seed = 84735)

ggplot(q10data, aes(x = type))+
  geom_density()

table(q10data$type)
head(q10data)
```

1.  According to the code above, there is a 95% prior chance that the *probability* of an article being real news is between what two values?

    ANS: .2 and .8

2.  Is there substantial evidence of a difference in the odds of the news being real for articles with and without an explanation point? Justify your response.

    ANS: There's a 90% posterior probability that odds of an article with an exclamation point being labeled as real is between .02 and .22 greater than when it does not have an exclamation point.

```{r}
exp(posterior_interval(q10mod1))
```

3.  Calculate and interpret the sensitivity of the model using 5-fold cross-validation.

    ANS: The logistic regression model has sensitivity equal to 92.4%. This means that 92% of all real labeled articles in the training set were correctly classified as a real article.

```{r}
classification_summary_cv(model = q10mod1, data = q10data, cutoff = .5, k = 5)
```

4.  In the chunk below fit a Naive Bayes classification model for the same variables. Then determine how you would classify an article whose title is 7 words long and does not contain an exclamation point.

    ANS: Real article

```{r}
mod2 <- naiveBayes(type ~ title_words + title_has_excl, data = q10data)
predict(mod2, data.frame(title_words = 7, title_has_excl = 'FALSE'))
```

5.  Is the Naive Bayes model more likely to correctly classify a new fake news article or a new real news article? Justify your answer.

    ANS: Sensitivity = .9; Specificity = .37. Since the model's sensitivity is much higher than it's specificity, the naive bayes model does a better job classifying real news articles. Hence, it is more likely to classify a new real news article.

```{r}
naive_classification_summary(mod2, data = q10data, y = 'type')
```
