---
title: "DSC 335 Quiz 6"
format: pdf
editor: visual
---

```{r, include=FALSE}
library(tidyverse)
library(rstan)
library(bayesplot)
library(bayesrules)
```

Name:

For this quiz we will consider a Normal-Normal Bayesian model with $Y\sim N(\mu,5^2)$ and $\mu\sim N(0,1^2)$. We observe 5 independent data observations: $Y_1=3, Y_2=7, Y_3=-4, Y_4=2, Y_5=-1$. The code chunk below gives the summary and plot of the true posterior distribution (helpful for checking your work).

```{r, eval=FALSE, echo=TRUE}
plot_normal_normal(0,1,5,mean(c(3,7,-4,2,-1)),5)
summarize_normal_normal(0,1,5,mean(c(3,7,-4,2,-1)),5)
```

1.  Using the code chunk below, approximate the posterior distribution using grid approximation. Fill in any missing code/values (indicated by *?*)

```{r, eval=FALSE, echo=TRUE}
# Step 1: Define a grid of mu values
grid_data   <- data.frame(mu_grid = seq(from = -10, to = 10, length=201))

# Step 2: Evaluate the prior & likelihood at each mu
grid_data <- grid_data |>  
  mutate(prior = dnorm(mu_grid, 0, 1),
         likelihood = dnorm(3, mu_grid, 5) * dnorm(7, mu_grid, 5) * dnorm(-4, mu_grid, 5) * dnorm(2, mu_grid, 5) * dnorm(-1, mu_grid, 5))

# Step 3: Approximate the posterior
grid_data <- grid_data |> 
  mutate(unnormalized = prior * likelihood,
         posterior = unnormalized / sum(unnormalized))

# Set the seed
set.seed(84735)

# Step 4: sample from the discretized posterior
post_sample <- sample_n(grid_data, size = 10000, 
                        weight = posterior, replace = T)

#plotting the simulated posterior
ggplot(post_sample, aes(x = mu_grid)) + 
  geom_histogram(aes(y =after_stat(density)), color = "white") +
  stat_function(fun = dnorm, args = list(0.2333333, 0.9128709))
```

2.  Using the code chunk below, approximate the posterior using MCMC.

```{r, eval=FALSE, echo=TRUE}
# STEP 1: DEFINE the model
nn_model <- "
  data {
    real Y[5];
  }
  parameters {
    real mu;
  }
  model {
    Y ~ normal(mu, 5);
    mu ~ normal(0, 1);
  }
"
# STEP 2: SIMULATE the posterior
nn_sim <- stan(model_code = nn_model, 
               data = list(Y = c(3, 7, -4, 2, -1)), 
               chains = 4, iter = 5000*2, seed = 84735)

# Density plot of the Markov chain values
mcmc_dens(nn_sim, pars = "mu") + 
  yaxis_text(TRUE) + 
  ylab("density") +
  stat_function(fun = dnorm, args = list(0.2333333, 0.9128709))


```
